Make manuscript figures

### 2021-10-28 scripts/R/make_manuscript_figures.rmd
mess with plot sizes

Define formatting
```{r}
diverging_palette <- "Set2"
gradient_palette <- "PiYG"
shared_theme <- theme_bw()
single_col_width <- 8.7  # cm
double_col_width <- 11.4  # cm

@@

png(
  filename = paste(FIGDIR, "model_figure.png", sep = "/"),
  width = double_col_width, height = single_col_width, units = "cm", res = 300)
  plot_grid(left_side, NULL, right_side, ncol = 3, rel_widths = c(1.5, 0.2, 1))
dev.off()

@@

# Plot RMSE
rmse_plot <- plotHeatmap(
        df = data.summary,
        N.sim = data.summary$N.reps[[1]],
        is.MLE = T,
        scale.limits = c(0, 1),
        legend.name = "RMSE",
        midpoint = 0.5,
        fill.hi = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[1],
        fill.lo = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[3],
        fill.mid = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[2],
        x.var = "alpha",
        y.var = "H2",
        fill.var = "mean.error",
        facet.x = "inference.method",
        facet.y = NA,
        is.oob.squish = F,
        is.real.scale = F,
        labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * italic('H'^2) * ")")) +
        theme(
                text = element_text(size = 8),
                panel.border = element_rect(colour = "black", size = 0.5, fill = NA),
                strip.background = element_rect(colour = "black", size = 0.5)) +
        geom_point(data = spvl_data, fill = "black")

@@

# Plot TPR
tpr_plot <- makeTPRPlot(
        df = data.summary %>% filter(inference.method %in% c(e_name, ehat_name, z_minus_zbar_name)),
        is.MLE = T,
        midpoint = 0.5,
        fill.lo = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[3],
        fill.hi = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[1],
        fill.mid = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[2]) +
        facet_grid(. ~ inference.method, labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * 'H'^2 * ")")) +
        theme(
                text = element_text(size = 8),
                panel.border = element_rect(colour = "black", size = 0.5, fill = NA),
                strip.background = element_rect(colour = "black", size = 0.5)) +
        geom_point(data = spvl_data, fill = "black")

top_row <- plot_grid(NULL, rmse_plot, rel_widths = c(1, 3.25), labels = c("", "A"))
png(filename = "figures/simulation_results.png", width = double_col_width, height = single_col_width, unit = "cm", res = 300)
plot_grid(top_row, tpr_plot, align = "v", axis = "tb", nrow = 2, labels = c("", "B"))
dev.off()
```

>>>>

Define formatting
```{r}
diverging_palette <- "Set2"
gradient_palette <- "PiYG"
shared_theme <- theme_bw()
linewidth <- 16.5  # cm
height <- 11  # cm

@@

png(
  filename = paste(FIGDIR, "model_figure.png", sep = "/"),
  width = linewidth, height = height, units = "cm", res = 300)
  plot_grid(left_side, NULL, right_side, ncol = 3, rel_widths = c(1.5, 0.2, 1))
dev.off()

@@

# Plot RMSE
rmse_plot <- plotHeatmap(
        df = data.summary,
        N.sim = data.summary$N.reps[[1]],
        is.MLE = T,
        scale.limits = c(0, 1),
        legend.name = "RMSE",
        midpoint = 0.5,
        fill.hi = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[1],
        fill.lo = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[3],
        fill.mid = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[2],
        x.var = "alpha",
        y.var = "H2",
        fill.var = "mean.error",
        facet.x = "inference.method",
        facet.y = NA,
        is.oob.squish = F,
        is.real.scale = F,
        labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90)) +
        geom_point(data = spvl_data, fill = "black")

@@

# Plot TPR
tpr_plot <- makeTPRPlot(
        df = data.summary %>% filter(inference.method %in% c(e_name, ehat_name, z_minus_zbar_name)),
        is.MLE = T,
        midpoint = 0.5,
        fill.lo = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[3],
        fill.hi = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[1],
        fill.mid = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[2]) +
        facet_grid(. ~ inference.method, labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * 'H'^2 * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90)) +
        geom_point(data = spvl_data, fill = "black")

top_row <- plot_grid(NULL, rmse_plot, rel_widths = c(1, 3.25), labels = c("", "A"))
png(filename = "figures/simulation_results.png", width = linewidth, height = height, unit = "cm", res = 300)
plot_grid(top_row, tpr_plot, align = "v", axis = "tb", nrow = 2, labels = c("", "B"))
dev.off()
```
